Project-I by Group ROME

### 2015-10-31 report/paper.tex
Added all files and final folder for upload with results

\documentclass{article} % For LaTeX2e
% We will use NIPS submission format
\usepackage{nips13submit_e,times}
% for hyperlinks
\usepackage{hyperref}
\usepackage{url}
% For figures
\usepackage{graphicx} 
\usepackage{subfigure} 
% math packages
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsopn}
\usepackage{ifthen}
\usepackage{natbib}

\title{Project-I by Group CITYNAME}

\author{
Corentin Tallec\\
Roman Shirochenko\\
EPFL \\
\texttt{corentin.tallec@epfl.ch} \\
}

@@

The results described here are summerized in the Figure \ref{fig:ridgeCurve}.

\subsection{Feature transformations}
As notified in a previous section, among all the feature at our disposal,
features 49 and 66 show distributions that ressemble the ditribution of the
output variable.

This led us to try and regress only on thos two features and polynomial
transformations of them. Using only those two features, we get an RMSE error
that is quite close to the one we notified when all the features are used. When
using polynomial features (up to degree 10), we basically get half the error
that we got using all the features. Those results were obtained using ridge
regression. As in the previous section, we obtained the RMSE as a function of
lambda, calculating both training and test errors using a kFold procedure with
$k=4$. The results are summarized in Figure \ref{fig:polyridgeCurve}, where, as
previously mentionned, we used as features only the two features and their
polynomial transformation with degree ranging from 1 to 10.

@@

\end{document}

>>>>

\documentclass{article} % For LaTeX2

% We will use NIPS submission format
\usepackage{nips13submit_e,times}
% for hyperlinks
\usepackage{hyperref}
\usepackage{url}
% For figures
\usepackage{graphicx} 
\usepackage{subfigure} 
% math packages
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsopn}
\usepackage{ifthen}
\usepackage{natbib}

\title{Project-I by Group ROME}

\author{
Roman Shirochenko\\
Corentin Tallec\\
EPFL \\
\texttt{roman.shirochenko@epfl.ch}\\
\texttt{corentin.tallec@epfl.ch} \\
}

@@

The results described here are summarized in the Figure \ref{fig:ridgeCurve}.

\subsection{Feature transformations}
As notified in a previous section, among all the feature at our disposal,
features 49 and 66 show distributions that resemble the distribution of the
output variable.

This led us to try and regress only on those two features and polynomial
transformations of them. Using only those two features, we get an RMSE error
that is quite close to the one we notified when all the features are used. When
using polynomial features (up to degree 10), we basically get half the error
that we got using all the features. Those results were obtained using ridge
regression. As in the previous section, we obtained the RMSE as a function of
lambda, calculating both training and test errors using a kFold procedure with
$k=4$. The results are summarized in Figure \ref{fig:polyridgeCurve}, where, as
previously mentioned, we used as features only the two features and their
polynomial transformation with degree ranging from 1 to 10.

@@

\section{Logistic Regression}
\subsection{Data Description}
Our second data set consisted of a train set, with an input and an output binary
variable respectively $\mathbf{X}$ and $\mathbf{y}$, composed of $N=1500$ data
samples, and a test set with only $\mathbf{X}$ variable observed and $N=1500$
data samples. $\mathbf{X}$ spans over $D=34$ features, among which 5 of them are
categorical, with number of categories ranging from 1 to 5.

Our goal is to produce binary classification predictions for test examples and approximate the
test error.

\subsection{Data visualization and cleaning}
Firstly, the data was visualized. The first thing we
did was to obtain a visualization of the data, showed in \ref{fig:boxplotX} and
\ref{fig:histY}. Those two figures led us to normalize both the input and the
output variable (normalizing the output variable allow us to have results that are
easier to interpret, as they are to be compared to values close to 1). No
obvious outliers are noticeable on the $\mathbf{y}$ histogram.

We performed featurewise analysis to notice that most of our real valued
variables have nearly gaussian distributions (or at least unimodal
distributions), which is not the case of our output variable. Figure
\ref{fig:cor1} shows how the output variable evolves as a function of the first
feature. This behaviour is what we notice on most variables, and thus shows no
clear correlations.
\end{document}
